Unimodular covers of 3-dimensional parallelepipeds and Cayley sums

### 2019-07-05 unimodular-covers.tex
added sketches of pictures

\usepackage{tikz-cd}
\usepackage{tikz}
\usetikzlibrary{matrix}
\usepackage{tkz-euclide}

@@

\begin{claim}\giulia{I think we need to treat separately the case where we deal with edges (these are easier, in any case, but I couldn't find a unification)}
The following inequalities hold, provided the segment in question is not an edge of the corresponding polytope:
\begin{align*}
\width_{f_q}(l) > i, \\
\width_{f_q}(r) > i, \\
\width_{f_p}(t) > i, \\
\width_{f_p}(b) > i.
\end{align*}
\end{claim}

@@

\begin{proof}
If, say, $b$ has positive slope and $t$ negative. Then since $t$ intersects the vertical line $x=0$ spanned by $p$ below $p_2$, and $b$ intersects it above $p_1$, the slopes of $b$ and $t$ imply that  $Q \cap \{x\ge 0\}$ is contained in the strip $-1<f_q(x)<i-1$, of width $i$. This cannot contain a translated copy of $r$, since $\width_{f_q}(r) >i$ .
\end{proof}

@@

\begin{proof}
\giulia{translate this into the width language!}
Since $t$ and $b$ both intersect $p$, these intersections form a vertical segment which has width w.r.t $f_q$ less than $i$, the width of $p$. The assumptions on the slopes implies that this is true for any vertical segment with endpoints in $b$ and $t$ to the right of this one, which is part (a).

For (b), if $r$ had negative slope, it would be impossible to fit a translated copy of $r$ in the right side of $Q$, because of (a): it would lie \giulia{finish, with picture}
\end{proof}

@@

>>>>

\usepackage{tikz-cd}
\usepackage{tikz}
\usetikzlibrary{matrix}
\usepackage{tkz-euclide}
\usetikzlibrary{intersections}
\usetkzobj{all}

@@

\begin{claim}\giulia{I think we need to treat separately the case where we deal with edges (these are easier, in any case, but I couldn't find a unification)}
The following inequalities hold, provided the segment in question is not an edge of the corresponding polytope:
\begin{align*}
\width_{f_q}(l) , 
\width_{f_q}(r) ,
\width_{f_p}(t) ,
\width_{f_p}(b) > i.
\end{align*}
\end{claim}

@@

\begin{proof}
If, say, $b$ has positive slope and $t$ negative. Then since $t$ intersects the vertical line $x=0$ spanned by $p$ below $p_2$, and $b$ intersects it above $p_1$, the slopes of $b$ and $t$ imply that  $Q \cap \{x\ge 0\}$ is contained in the strip $-1<f_q(x)<i-1$, of width $i$. This cannot contain a translated copy of $r$, since $\width_{f_q}(r) >i$ .
\end{proof}
\includegraphics[width=.7\textwidth]{Claim42.jpg}

@@

\begin{proof}

Since $t$ and $b$ both intersect $p$, these intersections form a vertical segment which has width w.r.t $f_q$ less than $i$, the width of $p$. The assumptions on the slopes implies that this is true for any vertical segment with endpoints in $b$ and $t$ to the right of this one, which is part (a).

For part (b), let $r = conv(u, v)$, with $\vec r=v-u$. If $r$ had negative slope, it would be impossible to fit a translated copy of $r$ in the right side of $Q$: $r$ would lie inside the region to the left of $u$ delimited by $t$, the horizontal line containing $u$ and the vertical line through $u$. We can observe that this triangular region has width w.r.t. $f_q$ less than $i$ by combining part (a), which implies that the vertical segment through $u$ between $t$ and $u$ has width w.r.t $f_q$ less than $i$, with the fact that $t$ has positive slope. 
\end{proof}
\includegraphics[ width=.7\textwidth]{Claim43.jpg}

@@

TRYING TO MODIFY this picture:

\begin{figure}[htb]
  \centering
\begin{tikzpicture}[mynode/.style={circle, inner sep=1.5pt, fill=red}, scale =
  .7]
%coordinate axes
   \tkzInit[xmax=3.5,ymax=3.5,xmin=-3.5,ymin=-3.5]
%        \tkzLabelX[orig=false,label options={font=\tiny}]
%        \tkzLabelY[orig=false,label options={font=\tiny}]
%        \tkzGrid
%        \tkzDrawX
%        \tkzDrawY

%edges b, t
  \node[mynode] (b1) at (-3,-2) {}; 
  \node[mynode] (b2) at (2, 0.2) {};  
  \node[mynode] (t1) at (-2.7, 1) {};  
  \node[mynode] (t2) at (1.6,0.7) {};  
  %\node[mynode] (E) at (-2,-1) {};  
  %\node[mynode] (F) at (-3,-3) {};

%p
  \node[mynode] (p1) at (0,-1) {}; 
  \node[mynode] (p2) at (0,1) {};

%q
  \node[mynode] (q1) at (-1,0) {}; 
  \node[mynode] (q2) at (1,0) {};

 % \draw[black] (A) -- (B) -- (C) -- (D) -- (E) -- (F) -- (A);
  \draw[name path = b, black] (b1) -- (b2); 
  \draw[name path = t, black] (t1) -- (t2);
  \draw[name path = p, black, thick] (p1) -- (p2);
  \draw[name path = q, black, thick] (q1) -- (q2);

 \tkzDrawLine[add=0.2 and 0.3, color=black, dashed](b1, b2);
  \tkzDrawLine[ add=0.3 and 0.4, color=black, dashed](t1, t2);
  \path [name intersections={of = p and b}];
  \coordinate (S)  at (intersection-1);

\end{tikzpicture}

%\centerline{\hfill $P$ \hfill\hfill $Q$ \hfill}

\end{figure}
